Databrary: A digital data library for sharing research video

### 2015-01-15 jcdl-15/paper.tex
more sentences, questionable

>>>>

% this is questionable...
Most existing research data repositories provide either unstructured storage of arbitrary files, or have rigorously structured schema that require contributors to properly extract and format contributions.
While the former is well suited for archival of entire datasets and general-purpose hosting of materials, it does not facilitate discoverability, understanding, or re-use across various datasets.
The latter, on the other hand, generate large-scale, homogonous data sources for meta- and re-analysis, but limited to specific domains and research questions, losing the full richness and innovation of the source materials and field.
% we're a hybrid?
